---
title: "Hatchery_perception_analysis"
author: "Katie Shelledy"
date: "2022-04-18"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load necessary libraries
```{r}
library("tm")
library("SnowballC")
library("wordcloud")
library("RColorBrewer")
library("syuzhet")
library("ggplot2")
library("cowplot")
```

Import Data
```{r}
rawdata <- read.csv("Perception.csv")
```

Data prep
```{r}
abstracts<-rawdata[,7]

# Load the data as a corpus
TextDoc <- Corpus(VectorSource(abstracts))

#Replacing "/", "@" and "|" with space
toSpace <- content_transformer(function (x , pattern ) gsub(pattern, " ", x))
TextDoc <- tm_map(TextDoc, toSpace, "/")
TextDoc <- tm_map(TextDoc, toSpace, "@")
TextDoc <- tm_map(TextDoc, toSpace, "\\|")
# Convert the text to lower case
TextDoc <- tm_map(TextDoc, content_transformer(tolower))
# Remove numbers
TextDoc <- tm_map(TextDoc, removeNumbers)
# Remove english common stopwords
TextDoc <- tm_map(TextDoc, removeWords, stopwords("english"))
# Remove punctuations
TextDoc <- tm_map(TextDoc, removePunctuation)

# Build a term-document matrix
TextDoc_dtm <- TermDocumentMatrix(TextDoc)

```

Word associations
```{r}
# Find associations with "hatchery" or similar
findFreqTerms(TextDoc_dtm, lowfreq = 10) #check for applicable words
keywords <- c("hatcheries", "hatchery", "hatcheryreared") # "farmed", "enhancement", "supplementation", "captive") #build list of key words
associations <- findAssocs(TextDoc_dtm, terms = keywords, corlimit = 0.5)
```

Create term list from words associated with "hatchery" or similar
```{r}
list<-as.data.frame(unlist(associations, use.names=TRUE))
list<-row.names(list)
list<-sub('hatcheries.', '', list)
list<-sub('hatchery.','', list)
#list<-sub('hatcheryreared.','', list)
#list<-sub('supplementation.','', list)
#list<-sub('captively.','', list)

```

Regular sentiment score
```{r}
syuzhet_vector <- get_sentiment(list, method="syuzhet")
# see the first row of the vector
head(syuzhet_vector)
# see summary statistics of the vector
summary(syuzhet_vector)
# If the number of the mean is closer to +1, that means it has a positive connotation, closer to -1 has a negative
```
NRC sentiment analysis: run nrc sentiment analysis to return data frame with each row classified as one of the following emotions, rather than a score: anger, anticipation, disgust, fear, joy, sadness, surprise, trust. It also counts the number of positive and negative emotions found in each row.
```{r}
sentiment <- get_nrc_sentiment(list)
head (sentiment,10)
```
Prep NRC data for graphing:
```{r}
#transpose
t_sentiment <- data.frame(t(sentiment))
#The function rowSums computes column sums across rows for each level of a grouping variable.
sent_sum <- data.frame(rowSums(t_sentiment[1:8]))##adjust numbers based on # obs in "sentiment"
#Transformation and cleaning
names(sent_sum)[1] <- "count"
sent_sum <- cbind("sentiment" = rownames(sent_sum), sent_sum)
rownames(sent_sum) <- NULL

#To get rid of the sum of the positive and negative counts for graph purposes
sent_graph <- sent_sum[9:10,]
```

Graphing sentiments
```{r}
#Plot Two - count of words associated with each sentiment as a percentage
ggplot(sent_graph, aes(x = sentiment, (y = count/sum(count)))) + 
  geom_bar(stat = "identity", color = "black", fill="grey50", alpha =0.25) + 
  ggtitle("Sentiment of words associated with hatcheries") + 
  labs(y = "% of words") + 
  theme_cowplot() + 
  scale_y_continuous(expand = expansion(mult = c(0,0.05)))


```

