---
title: "Code for Project (final)"
author: "Katie Shelledy"
date: "2022-11-01"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load necessary libraries:
```{r}
library("tm")
library("SnowballC")
library("wordcloud")
library("RColorBrewer")
library("syuzhet")
library("tidyverse")
library("cowplot")
library("DataCombine")
library("gridExtra")
library("ggpubr")
library("ggwordcloud")
```

Step 1: Upload applicable data sets
```{r}
rawdata <- read.csv("RawDataB.csv")
services <- read.csv("ServicesB.csv")
```

Step 2: Prep datasets (pare down, combine)
```{r}
##save important columns##
rawdata <- rawdata[,c("Paper_Number","Journal","Type_of_paper","Lead_author_discipline","Region")]

##remove unnecessary column##
services <- select(services,-"Service_in_my_words")
services <- services %>% mutate_all(na_if,"")

##merge dataframes for analysis
data <- merge(rawdata, services, by = "Paper_Number")

##remove old data frames from workspace##
rm(services)
```

Step 3. ES Distributions_set up data
```{r}
##Data_prep
data <- select(data, -c(CICES_division1, CICES_group1, CICES_class1, CICES_division2, CICES_group2, CICES_class2, CICES_division3, CICES_group3, CICES_class3))#remove columns that will make the code tedious

ES1<-select(data, c(Paper_Number:Type_of_interaction, CICES_section1:CICES_code1, EE_domain1:EE_code1))
ES2<-select(data, c(Paper_Number:Type_of_interaction, CICES_section2:CICES_code2, EE_domain2:EE_code2))
ES3<-select(data, c(Paper_Number:Type_of_interaction, CICES_section3:CICES_code3, EE_domain3:EE_code3))#Create three databases to separate ES counts

ES1 <- rename(ES1, "CICES_section" = CICES_section1, "CICES_code" = CICES_code1, "EE_domain" = EE_domain1, "EE_code" = EE_code1)
ES2 <- rename(ES2, "CICES_section" = CICES_section2, "CICES_code" = CICES_code2, "EE_domain" = EE_domain2, "EE_code" = EE_code2)
ES3 <- rename(ES3, "CICES_section" = CICES_section3, "CICES_code" = CICES_code3, "EE_domain" = EE_domain3, "EE_code" = EE_code3)#rename to have consistent column name

ES <- rbind(ES1, ES2, ES3)
rm(ES1,ES2,ES3)
```

Step 4: Rename CICES codes with meanings
```{r}
EScode <- data.frame(
  code = c("1.1.4.1","1.1.4.2","1.1.4.3","1.1.6.1","1.1.6.2","1.1.6.3","1.2.2.1","1.2.2.3","1.3.X.X","2.1.1.2","2.2.1.1","2.2.1.3","2.2.2.1","2.2.2.2","2.2.2.3","2.2.3.1","2.2.4.2","2.2.5.1","2.2.5.2","2.3.X.X","3.1.1.1","3.1.1.2","3.1.2.1","3.1.2.2","3.1.2.3","3.1.2.4","3.2.1.1","3.2.1.2","3.2.1.3","3.2.2.1","3.2.2.2","3.3.X.X"), 
  name = c( "nutrition","materials","energy","nutrition","materials","energy","biodiversity","novel biology","profit","C sequestration","erosion","water flow","pollination","seed dispersal","nursery","invasive species","soil quality","freshwater quality","marine water quality","other reg","active recreation","passive recreation","knowledge","education","heritage","aesthetic","symbol","religion","representation","existence","bequest","other cultural"))

ES <- FindReplace(data = ES, Var = "CICES_code", replaceData = EScode, from = "code", to = "name", exact = TRUE, vector = FALSE)

rm(EScode)
```

Figure 1: Summary Data_Characterizing Papers
```{r}
##Data Prep##
Journal <- count(rawdata, rawdata$Journal)#create a data table with journal counts
names(Journal) <- c("Journal", "n")#rename column title to get rid of long 
Jshort <- data.frame(
  long = c("Canadian Journal of Fisheries and Aquatic Sciences","Journal of the North American Benthological Society", "Environmental Biology of Fishes"), 
  short = c( "Can J Fish Aquat Sci","J North Am Benthol Soc", "Environ Biol Fishes")) ##create database to rename long journals
Journal <- FindReplace(data = Journal, Var = "Journal", replaceData = Jshort, from = "long", to = "short", exact = TRUE, vector = FALSE)##Rename long journals
rm(Jshort)##Delete database for renaming
Journal <- Journal[order(-Journal$n),] #sort into descending order
Journal <- Journal[Journal$n>4,]#remove journals with less than 4 papers

Paper <- count(rawdata, rawdata$Type_of_paper)#create a data table with counts for each paper type (review, case study, etc.)
names(Paper) <- c("Type", "n")#rename column title to get rid of long column name
###THIS NEXT BATCH OF CODE ADDS OVERLAPPING PAPER TYPES TOGETHER, so that there is one value for each paper type#####
Paper[Paper$Type=="Observational",2]<-Paper[Paper$Type=="Observational",2]+Paper[Paper$Type=="Observational & modelling",2]+Paper[Paper$Type=="Observational & experiment",2] ##observational_type
Paper[Paper$Type=="Modelling",2]<-Paper[Paper$Type=="Modelling",2]+Paper[Paper$Type=="Observational & modelling",2]+Paper[Paper$Type=="Experiment & modelling",2]+Paper[Paper$Type=="Review & modelling",2]##Modelling_type
Paper[Paper$Type=="Review",2]<-Paper[Paper$Type=="Review",2]+Paper[Paper$Type=="Perspective & review",2]+Paper[Paper$Type=="Review & case study",2]+Paper[Paper$Type=="Review & modelling",2]##Review_type
Paper[Paper$Type=="Experiment",2]<-Paper[Paper$Type=="Experiment",2]+Paper[Paper$Type=="Experiment & modelling",2]+Paper[Paper$Type=="Observational & experiment",2]##experiment_type
Paper[Paper$Type=="Case study",2]<-Paper[Paper$Type=="Case study",2]+Paper[Paper$Type=="Multiple case studies",2]+Paper[Paper$Type=="Review & case study",2]##Case_study_type
Paper[Paper=="Perspective & review"] <- "Perspective"
Paper <- subset(Paper, Type != "Experiment & modelling")
Paper <- subset(Paper, Type != "Observational & modelling")
Paper <- subset(Paper, Type != "Observational & experiment")
Paper <- subset(Paper, Type != "Multiple case studies")
Paper <- subset(Paper, Type != "Review & case study")
Paper <- subset(Paper, Type != "Review & modelling")
Paper <- Paper[order(-Paper$n),] #sort into descending order

Location <- count(rawdata, rawdata$Region)#create a data table with Locations
names(Location) <- c("Location", "n")#rename column title to get rid of long column name
Location <- Location[order(-Location$n),] #sort into descending order
Location <- subset(Location, Location!="N/A" & Location!="Pacific")

#Plot all together GGPLOT ##
G1 <- ggplot(Location, aes(x=fct_inorder(Location), y=n))+ 
  geom_bar(stat = "identity", color = "black", fill = "grey50", alpha = 0.25) + 
  theme_cowplot() + 
  xlab("Location") + 
  ylab("Paper count") + 
  theme(axis.text=element_text(size=16), axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1), axis.title=element_text(size = 18, face = "bold")) + 
  scale_y_continuous(expand = expansion(mult = c(0, 0.05)))
  
G2 <- ggplot(Paper, aes(x=fct_inorder(Type), y=n))+ geom_bar(stat = "identity", color = "black", fill = "grey50", alpha = 0.25) + theme_cowplot() + xlab("Study type")+ theme(axis.text=element_text(size=16), axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1), axis.title=element_text(size = 18, face = "bold"), axis.title.y=element_blank()) + scale_y_continuous(expand = expansion(mult = c(0, 0.05)))

G3 <- ggplot(Journal, aes(x=fct_inorder(Journal), y=n))+ geom_bar(stat = "identity", color = "black", fill = "grey50", alpha = 0.25) + theme_cowplot() + xlab("Journal") + theme(axis.text=element_text(size=16), axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1), axis.title=element_text(size = 18, face = "bold"), axis.title.y=element_blank()) + scale_y_continuous(expand = expansion(mult = c(0, 0.05)))

ggarrange(G1, G2,
          labels = c("A", "B"),
          ncol = 2, nrow =1,
          align = "h", font.label = list(size = 16))

#helpful website: https://rpkgs.datanovia.com/ggpubr/reference/ggarrange.html
```

Figure 2: ES overall distribution across domains

2.1: Data prep
```{r}
h.CICES <- ES %>% group_by(CICES_section) %>% count(Hatchery_fish, sort = TRUE)
h.CICES <- subset(h.CICES, Hatchery_fish != "No")
h.CICES <- subset(h.CICES, CICES_section != "N/A")

h.EE <- ES %>% group_by(EE_domain) %>% count(Hatchery_fish)
h.EE <- subset(h.EE, Hatchery_fish != "No")
h.EE <- subset(h.EE, EE_domain != "N/A")
```

2.2: Create graphs
```{r}
hFWC <- ggplot() + 
  geom_bar(data=ES[complete.cases(ES[, "CICES_section"]), ], aes(fct_inorder(CICES_section), fill = Category), alpha = 0.7, color = "black", width = 0.5) + 
  scale_y_continuous(expand = expansion(mult = c(0, 0.05))) + 
  theme_cowplot() + 
  theme(legend.title=element_blank(), axis.title=element_text(size=18, face = "bold"), axis.title.y=element_blank(), axis.title.x=element_blank(), axis.text.x=element_text(hjust=0.75), axis.text=element_text(size=20), legend.text=element_text(size = 20)) + 
  scale_x_discrete() +
  scale_fill_manual(values = c("darksalmon", "deepskyblue4", "plum1"), breaks = c("socio", "eco", "both")) +
  geom_bar(data = h.CICES, aes(x=CICES_section, y=n, color = "Hatchery"), width = 1, size = 1.5, alpha = 0.01, stat = "identity") +
  scale_color_manual(values = c(Hatchery = "red")) +
  coord_flip() 

hFWE <- ggplot() + 
  geom_bar(data=ES[complete.cases(ES[, "EE_domain"]), ], aes(fct_inorder(EE_domain), fill = Category), alpha = 0.7, color = "black", width = 0.5) + 
  scale_y_continuous(expand = expansion(mult = c(0, 0.05))) + 
  theme_cowplot() +
  theme(axis.title=element_text(size=18, face = "bold"), axis.title.y = element_blank(), axis.text.x=element_text(hjust=0.75), axis.text=element_text(size=20)) +
  scale_x_discrete() +
  scale_fill_manual(values = c("plum1", "deepskyblue4", "darksalmon")) +
  geom_bar(data = h.EE, aes(x=EE_domain, y=n), width = 1, size = 1.5, alpha = 0.01, color = "red", stat = "identity") +
  coord_flip() + 
  ylab("count")
```

2.3: Create paneled graphic
```{r}
ggarrange(hFWC, hFWE, 
          labels = c("CICES", "EEScF"),
          common.legend = TRUE, legend = "bottom",
          ncol = 1, nrow = 2, align = "v",
          font.label = list(size = 18),
          heights = c(3,5))

##print default dimensions
```

Figures 3-4: ES distribution within each framewor

3-4.1: Rename long codes to make graphs easier to read
```{r}
EScode <- data.frame(
  original = c("Processing, Preserving, Cooking", "Indigenous Management Systems", "Indigenous Laws, Government & Institutions", "Passing to Future Generations", "Gatherings, Ceremonies", "Indigenous Commercial Fisheries", "Traditional Values", "Traditional Knowledge", "Spiritual & Belief Systems", "Treaties & Agreements"), 
  shortened = c("Process, Cook", "Indig Manag Sys", "Indig Law & Gov", "Future Gen", "Ceremonies", "Indig Comm Fish", "Trad Values", "Trad Knowledge", "Belief Systems", "Treaties"))

ES <- FindReplace(data = ES, Var = "EE_code", replaceData = EScode, from = "original", to = "shortened", exact = TRUE, vector = FALSE)

rm(EScode)
```

3-4.2: Create sub-data tables for graphing purposes
```{r}
###For ES dist
PES <- ES[ES$CICES_section=="Provisioning ",]#select for specific values
PES <- PES[complete.cases(PES[, "CICES_section"]), ]##remove NAs

RES <- ES[ES$CICES_section=="Regulation & Maintenance ",]
RES <- RES[complete.cases(RES[, "CICES_section"]), ]

CES <- ES[ES$CICES_section=="Cultural ",]
CES <- CES[complete.cases(CES[, "CICES_section"]), ]

KEES <- ES[ES$EE_domain=="Knowledge & Practices",]
KEES <- KEES[complete.cases(KEES[, "EE_domain"]), ]

LEES <- ES[ES$EE_domain=="Livelihood",]
LEES <- LEES[complete.cases(LEES[, "EE_domain"]), ]

IEES <- ES[ES$EE_domain=="Indigenous Management",]
IEES <- IEES[complete.cases(IEES[, "EE_domain"]), ]

SEES <- ES[ES$EE_domain=="Social",]
SEES <- SEES[complete.cases(SEES[, "EE_domain"]), ]

HEES <- ES[ES$EE_domain=="Health",]
HEES <- HEES[complete.cases(HEES[, "EE_domain"]), ]

###For hatchery count DIST
h.CICES <- ES %>% group_by(CICES_code) %>% count(Hatchery_fish)##add CICES_data
h.CICES <- subset(h.CICES, Hatchery_fish != "No")
h.CICES <- subset(h.CICES, CICES_code != "N/A")

h.EE <- ES %>% group_by(EE_code) %>% count(Hatchery_fish)
h.EE <- subset(h.EE, Hatchery_fish != "No")
h.EE <- subset(h.EE, EE_code != "N/A")

##further subsets for hatchery ES mapping
Ph.CICES <- h.CICES[h.CICES$CICES_code %in% c("energy", "materials", "novel biology", "nutrition","profit"), ]
Rh.CICES <- h.CICES[h.CICES$CICES_code %in% c("freshwater quality", "invasive species", "nursery", "soil quality"), ]
Ch.CICES <- h.CICES[h.CICES$CICES_code %>% c("active recreation", "aesthetic", "education", "existence", "heritage", "knowledge", "other", "religion"), ]

Kh.EE <- h.EE[h.EE$EE_code %in% c("Fishing Activities"), ]
Lh.EE <- h.EE[h.EE$EE_code %in% c("Food", "Indig Comm Fish"),]
Ih.EE <- h.EE[h.EE$EE_code %in% c("Treaties"),]
Sh.EE <- h.EE[h.EE$EE_code %in% c("Ceremonies"),]
#Hh.EE None for health
```

3-4.3: Create graphs
```{r}
CICES1 <- ggplot() + 
  geom_bar(data=PES, color = "black", aes(x=CICES_code, fill = Category), width = 0.5, alpha =0.7) + 
  scale_y_continuous(expand = expansion(mult = c(0, 0.05))) + 
  theme_cowplot() + 
  theme(axis.text=element_text(size=16), axis.title=element_text(size=18), legend.text = element_text(size=16), legend.title = element_blank(),axis.title.y=element_blank(), axis.title.x=element_blank()) + 
  coord_flip() +
  scale_fill_manual(values = c("darksalmon", "deepskyblue4", "plum1"), breaks = c("socio", "eco", "both")) +
  geom_bar(data = Ph.CICES, aes(x=CICES_code, y=n, color = "Hatchery"), size = 1.5, width = 1, alpha = 0.01, stat = "identity") +
  scale_color_manual(values = c(Hatchery = "red"))

CICES2 <- ggplot() + 
  geom_bar(data=RES, aes(x=CICES_code, fill = Category), color = "black", width = 0.5, alpha = 0.7) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.05))) + 
  theme_cowplot() +
  theme(axis.text=element_text(size=16), axis.title=element_text(size=18), legend.text = element_text(size=16), legend.title = element_blank(), axis.text.x = element_text(), axis.title.y=element_blank(), axis.title.x=element_blank()) + 
  coord_flip() +
  scale_fill_manual(values = c("plum1", "deepskyblue4", "darksalmon")) +
  geom_bar(data = Rh.CICES, aes(x=CICES_code, y=n, color = "Hatchery"), width = 1, size = 1.5, alpha = 0.01, stat = "identity") +
  scale_color_manual(values = c(Hatchery = "red"))

CICES3 <- ggplot() + 
  geom_bar(data=CES, aes(x=CICES_code, fill = Category), color = "black", width = 0.5, alpha = 0.7) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.05))) + 
  theme_cowplot() +
  theme(axis.text=element_text(size=16), axis.title=element_text(size=18), legend.text = element_text(size=16), legend.title = element_blank(), axis.title.y=element_blank()) + 
  ylab("count")+ 
  coord_flip() +
  scale_fill_manual(values = c("plum1", "deepskyblue4", "darksalmon")) +
  geom_bar(data = Ch.CICES, aes(x=CICES_code, y=n, color = "Hatchery"), width = 1, size = 1.5, alpha = 0.01, stat = "identity") +
  scale_color_manual(values = c(Hatchery = "red"))

EE1 <- ggplot() + 
  geom_bar(data=KEES, aes(x=EE_code, fill = Category), color = "black", width = 0.5, alpha = 0.7) + 
  scale_y_continuous(expand = expansion(mult = c(0, 0.05))) + 
  theme_cowplot() + 
  theme(axis.text=element_text(size=16), axis.title=element_text(size=18), legend.text = element_text(size=16), legend.title=element_blank(), axis.title.y=element_blank()) + 
  ylab("count") + coord_flip() +
  scale_fill_manual(values = c("darksalmon", "deepskyblue4", "plum1"), breaks = c("socio", "eco", "both")) + 
  geom_bar(data = Kh.EE, aes(x=EE_code, y=n, color = "Hatchery"), width = 1, size =1.5, alpha = 0.01, stat = "identity") +
  scale_color_manual(values = c(Hatchery = "red"))

EE2 <- ggplot() + 
  geom_bar(data=LEES, aes(x=EE_code, fill = Category), color = "black",  width = 0.5, alpha = 0.7, show.legend = FALSE) + 
  scale_y_continuous(expand = expansion(mult = c(0, 0.05))) + 
  theme_cowplot() + 
  theme(axis.text=element_text(size=16), axis.title=element_text(size=18), legend.text = element_text(size=16), axis.title.y = element_blank(), axis.title.x=element_blank()) + 
  coord_flip() +
  scale_fill_manual(values = c("plum1", "darksalmon")) +
  geom_bar(data = Lh.EE, aes(x=EE_code, y=n), width = 1, size =1.5, alpha = 0.01, color = "red", stat = "identity")

EE3 <- ggplot() + 
  geom_bar(data=IEES, aes(x=EE_code, fill = Category), color = "black", width = 0.5, alpha = 0.7, show.legend = FALSE) + 
  scale_y_continuous(expand = expansion(mult = c(0, 0.05))) + 
  theme_cowplot() + 
  theme(axis.text=element_text(size=16), axis.title=element_text(size=18), legend.text = element_text(size=16), axis.title.y=element_blank(), axis.title.x=element_blank()) +
  coord_flip() + 
  scale_fill_manual(values = c("darksalmon")) +
  geom_bar(data = Ih.EE, aes(x=EE_code, y=n), width = 1, size = 1.5, alpha = 0.01, color = "red", stat = "identity")

EE4 <- ggplot() + 
  geom_bar(data=SEES, aes(x=EE_code, fill = Category), color = "black", width = 0.5, alpha = 0.7, show.legend = FALSE) + 
  scale_y_continuous(expand = expansion(mult = c(0, 0.05))) + 
  theme_cowplot() + 
  theme(axis.text=element_text(size=16), axis.title=element_text(size=18), legend.text = element_text(size=16), axis.title.y=element_blank(), axis.title.x=element_blank()) + 
  coord_flip() +
  scale_fill_manual(values = c("darksalmon")) +
  geom_bar(data = Sh.EE, aes(x=EE_code, y=n), width = 1, size=1.5, alpha = 0.01, color = "red", stat = "identity")

EE5 <- ggplot() + 
  geom_bar(data=HEES, aes(x=EE_code, fill = Category), color = "black", width = 0.5, alpha = 0.7, show.legend = FALSE) + 
  scale_y_continuous(expand = expansion(mult = c(0, 0.05))) + 
  theme_cowplot() + 
  theme(axis.text=element_text(size=16), axis.title=element_text(size=18), legend.text = element_text(size=16), axis.title.y=element_blank()) + 
  xlab("count") +
  coord_flip() + 
  scale_fill_manual(values = c("darksalmon")) 
```

3-4.4: Create panelled graphic
```{r}
##Zoom in on CICES FW SIZE500 x 750 
ggarrange(CICES1, CICES2, CICES3,
          labels = c("Provisioning", "Regulation/Maintenance", "Cultural"),
          hjust=0, vjust=0.8,
          ncol = 1, nrow =3, align = "v",
          common.legend = TRUE, legend = "bottom",
          font.label = list(size=18),
          heights = c(1,2,2))

##Zoom in on EE FW size 1000x750
ggarrange(EE4, EE2, EE3, EE5, EE1,
          labels = c("Social", "Livelihood", "Indig Management", "Health", "Knowledge & Practices"),
          hjust=0, vjust=0.8,
          ncol = 2, nrow = 3, align = "v",
          common.legend = TRUE, legend = "bottom",
          font.label = list(size=18),
          heights = c(1,1,2))

#refer to https://search.r-project.org/CRAN/refmans/ggpubr/html/ggarrange.html for label positions
```

Figure 5: Word clouds

5.1: Data prep
```{r}
## Subset data to include only Category and Sentence_about_service
word.clouds <- select(data, c("Category","Sentence_about_service"))

##Create separate data frames for socio and eco categories
socio.clouds <- word.clouds[word.clouds$Category == 'both' | word.clouds$Category == 'socio', ]
socio <- socio.clouds$Sentence_about_service
eco.clouds <- word.clouds[word.clouds$Category == 'both' | word.clouds$Category == 'eco', ]
eco <- eco.clouds$Sentence_about_service

##Prep cumulative word.cloud dataframe for analysis
all <- word.clouds$Sentence_about_service

## Load the data as a corpus
TextDoc_all <- Corpus(VectorSource(all))
TextDoc_socio <- Corpus(VectorSource(socio))
TextDoc_eco <- Corpus(VectorSource(eco))

#Replacing "/", "@" and "|" with space
toSpace <- content_transformer(function (x , pattern ) gsub(pattern, " ", x))

TextDoc_all <- tm_map(TextDoc_all, toSpace, "/")
TextDoc_all <- tm_map(TextDoc_all, toSpace, "@")
TextDoc_all <- tm_map(TextDoc_all, toSpace, "\\|")

TextDoc_socio <- tm_map(TextDoc_socio, toSpace, "/")
TextDoc_socio <- tm_map(TextDoc_socio, toSpace, "@")
TextDoc_socio <- tm_map(TextDoc_socio, toSpace, "\\|")

TextDoc_eco <- tm_map(TextDoc_eco, toSpace, "/")
TextDoc_eco <- tm_map(TextDoc_eco, toSpace, "@")
TextDoc_eco <- tm_map(TextDoc_eco, toSpace, "\\|")

# Convert the text to lower case
TextDoc_all <- tm_map(TextDoc_all, content_transformer(tolower))
TextDoc_socio <- tm_map(TextDoc_socio, content_transformer(tolower))
TextDoc_eco <- tm_map(TextDoc_eco, content_transformer(tolower))
# Remove numbers
TextDoc_all <- tm_map(TextDoc_all, removeNumbers)
TextDoc_socio <- tm_map(TextDoc_socio, removeNumbers)
TextDoc_eco <- tm_map(TextDoc_eco, removeNumbers)
# Remove english common stopwords
TextDoc_all <- tm_map(TextDoc_all, removeWords, stopwords("english"))
TextDoc_socio <- tm_map(TextDoc_socio, removeWords, stopwords("english"))
TextDoc_eco <- tm_map(TextDoc_eco, removeWords, stopwords("english"))
# Remove words without meaning
TextDoc_all <- tm_map(TextDoc_all, removeWords, c("also", "salmon"))
TextDoc_socio <- tm_map(TextDoc_socio, removeWords, c("also", "salmon"))
TextDoc_eco <- tm_map(TextDoc_eco, removeWords, c("also", "salmon"))
# Remove punctuations
TextDoc_all <- tm_map(TextDoc_all, removePunctuation)
TextDoc_socio <- tm_map(TextDoc_socio, removePunctuation)
TextDoc_eco <- tm_map(TextDoc_eco, removePunctuation)

# Build a term-document matrix
TextDoc_all_dtm <- TermDocumentMatrix(TextDoc_all)
dtm_all_m <- as.matrix(TextDoc_all_dtm)
TextDoc_socio_dtm <- TermDocumentMatrix(TextDoc_socio)
dtm_socio_m <- as.matrix(TextDoc_socio_dtm)
TextDoc_eco_dtm <- TermDocumentMatrix(TextDoc_eco)
dtm_eco_m <- as.matrix(TextDoc_eco_dtm)
# Sort by descearing value of frequency
dtm_all_v <- sort(rowSums(dtm_all_m),decreasing=TRUE)
word_freq_all <- data.frame(word = names(dtm_all_v),freq=dtm_all_v)
dtm_socio_v <- sort(rowSums(dtm_socio_m),decreasing=TRUE)
word_freq_socio <- data.frame(word = names(dtm_socio_v),freq=dtm_socio_v)
dtm_eco_v <- sort(rowSums(dtm_eco_m),decreasing=TRUE)
word_freq_eco <- data.frame(word = names(dtm_eco_v),freq=dtm_eco_v)

# Display the top 10 most frequent words
head(word_freq_all, 10)
```

5.2: Make word clouds
```{r}
#generate word cloud
word_freq_eco$word=str_replace_all(word_freq_eco$word,"[^[:graph:]]", " ")
eco.plot <- ggplot(data = word_freq_eco[1:30,], 
       aes(label = word, size = freq, col = freq)) + 
  geom_text_wordcloud(rm_outside = TRUE, max_steps = 1,
                      grid_size = 1, eccentricity = .9, show.legend = TRUE)+
  scale_size_area(max_size = 14)+
  theme_minimal() + 
  theme(legend.title=element_blank(), 
        legend.position="bottom", legend.justification = "right",
        legend.text = element_text(size=16)) + 
  scale_color_gradient(low="gray50", high = "gray0", guide = "none")

word_freq_socio$word=str_replace_all(word_freq_socio$word,"[^[:graph:]]", " ")
word_freq_socio <- subset(word_freq_socio, word != "–")
socio.plot <- ggplot(data = word_freq_socio[1:30,], 
                    aes(label = word, size = freq, col = freq)) + 
  geom_text_wordcloud(rm_outside = TRUE, max_steps = 1,
                      grid_size = 1, eccentricity = .9, show.legend = TRUE)+
  scale_size_area(max_size = 14)+
  theme_minimal() +
  theme(legend.title=element_blank(), 
        legend.position = "bottom", legend.justification = "right",
        legend.text = element_text(size = 16)) +
  scale_color_gradient(low="gray50", high = "gray0", guide = "none")

```

5.3: Make word clouds appear on one graphic
```{r}
##arrange word clouds on one graphic

ggarrange(eco.plot, socio.plot,
          labels = c("A", "B"), font.label = list(size = 18, face = "bold"), 
          ncol = 2, nrow = 1)
```

Figure 6: Comparison of frameworks
```{r}
#data prep

EScode <- data.frame(
  original = c("Processing, Preserving, Cooking", "Indigenous Management Systems", "Indigenous Laws, Government & Institutions", "Passing to Future Generations", "Gatherings, Ceremonies", "Indigenous Commercial Fisheries", "Traditional Knowledge", "Spiritual & Belief Systems", "Treaties & Agreements"), 
  shortened = c("Process, Cook", "Indig Manag Sys", "Indig Law & Gov", "Future Gen", "Ceremonies", "Indig Comm Fish", "Trad Knowledge", "Belief Systems", "Treaties"))

ES <- FindReplace(data = ES, Var = "EE_code", replaceData = EScode, from = "original", to = "shortened", exact = TRUE, vector = FALSE)

rm(EScode)

EScode <- data.frame(
  original = c("Indigenous Management"), 
  shortened = c("Indig Manag"))

ES <- FindReplace(data = ES, Var = "EE_domain", replaceData = EScode, from = "original", to = "shortened", exact = TRUE, vector = FALSE)

rm(EScode)

ES<-ES[order(ES$EE_domain),]#order based on EE_domain
ES<-ES[order(ES$CICES_section),] ##and cICES_section

ES <- na.omit(ES) #remove NAs for graphing

##graphing

ggplot(ES, aes(x=EE_code, y=CICES_code))+ geom_count(aes(alpha=0.5,color=Hatchery_fish))+
  scale_color_manual(values=c("gray40", "red"))+
  theme_cowplot()+ 
  theme(axis.text=element_text(size=16), axis.title=element_text(size=18), legend.text=element_text(size=16), axis.text.x=element_text(angle=90, vjust=0.5, hjust=1), axis.text.y=element_text(lineheight = 0.5))+
  facet_grid(CICES_section ~ EE_domain, scales="free", space = "free") + theme(strip.text=element_text(size=10)) +
  ylab("CICES service") + xlab("EEScF value") + guides(alpha="none")
#600 height by 1000 width

```
